Democratizing Secure Two-Party Computation

### 2017-10-22 OaklandSubmission/ld.tex
some text for target language and semantics

\subsubsection{Target language}

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Secret label} & m &::=& \mathcal{A} \mid \mathcal{B}\\
    \ftext{Label} & \ell &::=& \mathcal{P} \mid m\\
    \ftext{Type} & \tau &::=& \sigma^{\ell} \mid \sigma^{\ell}[n]\\
    \ftext{Expression} & \widetilde{e} &::=& c \mid x \mid \widetilde{e_{1}} +_{\ell} \widetilde{e_{2}} \mid \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}} \\
    & & \mid & \lcond{\ell}{{\widetilde{e}}}{{\widetilde{e_{1}}}}{{\widetilde{e_{2}}}} \mid x[\widetilde{e}] \mid [\overline{\widetilde{e_{i}}}]_{n} \mid \kw{in}^{m}_{j} \mid \widetilde{e} \rhd m\\
    \ftext{Statement} & \widetilde{s} &::=& \tau\:x = \widetilde{e} \mid x := \widetilde{e} \mid \dots \mid \widetilde{s_{1}}; \widetilde{s_{2}} \mid \dots\\
  \end{array}
  \]
\label{fig:tgtlang}
\caption{Target language}
\end{figure}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & r &&\\
    \ftext{Circuit gate} & \kappa & ::= & r \mid \kw{in}^{m}_{j} \mid \kw{add}\:\kappa_{1}\:\kappa_{2} \mid \kw{gt}\:\kappa_{1}\:\kappa_{2}\\
    & & \mid & \kw{mux}\:\kappa\:\kappa_{1}\:\kappa_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \widetilde{w} & ::= & c \mid \kappa\\
    \ftext{Value} & \widetilde{v} & ::= & \widetilde{w} \mid [\overline{\widetilde{w}_{i}}]_{n}\\
    \ftext{Circuit} & \chi & ::= & \cdot \mid \kw{bind}\:\kappa\:r \mid \kw{out}\:\kappa \mid \kappa_{1}; \kappa_{2}
  \end{array}
  \]
\label{fig:tgtruntime}
\caption{Target runtime}
\end{figure}

@@

\end{array}
  \]
\label{fig:tgtsem}
\caption{Target semantics (selected rules)}
\end{figure}

>>>>

@@

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Secret label} & m &::=& \mathcal{A} \mid \mathcal{B}\\
    \ftext{Label} & \ell &::=& \mathcal{P} \mid m\\
    \ftext{Type} & \tau &::=& \sigma^{\ell} \mid \sigma^{\ell}[n]\\
    \ftext{Expression} & \widetilde{e} &::=& c \mid x \mid \widetilde{e_{1}} +_{\ell} \widetilde{e_{2}} \mid \widetilde{e_{1}} >_{\ell} \widetilde{e_{2}} \\
    & & \mid & \lcond{\ell}{{\widetilde{e}}}{{\widetilde{e_{1}}}}{{\widetilde{e_{2}}}} \mid x[\widetilde{e}] \mid [\overline{\widetilde{e_{i}}}]_{n} \mid \kw{in}^{m}_{j} \mid \widetilde{e} \rhd m\\
    \ftext{Statement} & \widetilde{s} &::=& \tau\:x = \widetilde{e} \mid x := \widetilde{e} \mid \dots \mid \widetilde{s_{1}}; \widetilde{s_{2}} \mid \dots\\
  \end{array}
  \]
\caption{Target language}
\label{fig:tgtlang}
\end{figure}

\begin{figure}
  \small
  \[
  \begin{array}{rrcl}
    \ftext{Wire id} & r &&\\
    \ftext{Circuit gate} & \kappa & ::= & r \mid \kw{in}^{m}_{j} \mid \kw{add}\:\kappa_{1}\:\kappa_{2} \mid \kw{gt}\:\kappa_{1}\:\kappa_{2}\\
    & & \mid & \kw{mux}\:\kappa\:\kappa_{1}\:\kappa_{2} \mid \widetilde{w} \rhd m\\
    \ftext{Base value} & \widetilde{w} & ::= & c \mid r\\
    \ftext{Value} & \widetilde{v} & ::= & \widetilde{w} \mid \kappa \mid [\overline{\widetilde{w}_{i}}]_{n}\\
    \ftext{Runtime environment} & \widetilde{\rho} & ::= & \cdot \mid \widetilde{\rho}[x \mapsto \widetilde{v}]\\
    \ftext{Circuit} & \chi & ::= & \cdot \mid \kw{bind}\:\kappa\:r \mid \kw{out}\:\kappa \mid \kappa_{1}; \kappa_{2}
  \end{array}
  \]
\caption{Target runtime}
\label{fig:tgtruntime}
\end{figure}

@@

\end{array}
  \]
\caption{Target semantics (selected rules)}
\label{fig:tgtsem}
\end{figure}

\subsubsection*{Target language} Figure~\ref{fig:tgtlang} shows the
target language of our compiler. The syntax follows that of the source
languag, except that the types and operators are \emph{labeled}. Below
we mainly focus on the bits that are different from the source
language.

Labels $\ell$ consist of secret labels $\mathcal{A}$ and
$\mathcal{B}$, denoting the arithmetic and boolean shared secrets
resp., and the public label $\mathcal{P}$. Types $\tau$ are then
labeled base types $\sigma^{\ell}$ and arrays of labeled base types
$\sigma^{\ell}[n]$.

Most of the expression forms $\widetilde{e}$ are same as $e$, except
that the binary operators, and the conditional forms
are annotated with label $\ell$, denoting how the operators should be
evaluated ($\mathcal{P}$ for in-clear, and $\mathcal{A}$ and
$\mathcal{B}$ for using arithmetic or boolean circuits resp.). The
form $\widetilde{e} \rhd m$ denotes coercing $\widetilde{e}$ to be
$m$-secret shared. The statements $\widetilde{s}$ are analogous to
$s$.

The target semantics models the semantics of the code output by
our compiler (C++ code in our implementation). It computes over the
public parts of the program, emitting a circuit that can later be
evaluated using a cryptographic MPC protocol. Crucially, this phase of
the semantics does not have access to the secrets.

Figure~\ref{fig:tgtruntime} shows the runtime syntax. A wire id range
$r$ denotes a set of circuit wires that carry the value of a secret
shared variable in the output circuit. Circuit gates $\kappa$ are
$r$, input gates, \kw{add}, \kw{gt}, and \kw{mux} gates, and coerce
gates $\widetilde{w} \rhd m$. Target values $\widetilde{v}$ then
consist of base values $c$ and $r$, circuit gates $\kappa$, and arrays
of base values.

Figure~\ref{fig:tgtsem} shows the judgments for the target
semantics. We first focus on the expression evaluation judgment
$\widetilde{\rho} \vdash \widetilde{e} \Downarrow
\widetilde{v}$. Rules ({\sc{S-PAdd}}) and ({\sc{S-SAdd}}) illustrate
the significance of the operator labels. In particular, the rule
({\sc{S-PAdd}}) evaluates a public addition $\widetilde{e_{1}}
+_{\mathcal{P}} \widetilde{e_{2}}$ to $n_{1} + n_{2}$, similar to the
source language. In contrast, the rule
({\sc{S-SAdd}}) evaluates a secret addition $\widetilde{e_{1}}
+_{\mathcal{A}} \widetilde{e_{2}}$, using an arithmetic add
gate, to $\kw{add}\:\kappa_{1}\:\kappa_{2}$. Since our compiler
compiles secret add operations to arithmetic gates, the target
expressions from our compiler never have $\widetilde{e_{1}}
+_{\mathcal{B}} \widetilde{e_{2}}$ (we present the compilation rules
later in the section).
